Bandit Multiclass Linear Classification: \\ Efficient Algorithms for the Separable Case

### 2019-05-03 ICML-camera-ready/from-weak-separability-to-strong-separability.tex

Consider the classical real separable Hilbert space $\ell_2 = \{ x \in \R^\infty
~:~ \sum_{i=1}^\infty x_i^2 < + \infty \}$ equipped with the standard inner
product $\ip{x}{x'}_{\ell_2} = \sum_{i=1}^\infty x_i x'_i$. If we index the
coordinates of $\ell_2$ by $d$-tuples $(\alpha_1, \alpha_2, \dots, \alpha_d)$ of
non-negative integers, the feature map that corresponds to $k$ is $\phi: \B(\zero,1)
\to \ell_2$,
\begin{align}
\begin{split}
&\left(\phi(x_1, x_2, \dots, x_d)\right)_{(\alpha_1, \alpha_2, \dots, \alpha_d)} = \\
& x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d} \cdot \sqrt{2^{-(\alpha_1 + \alpha_2 + \dots + \alpha_d)} \binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots, \alpha_d}}
\end{split}
\label{equation:phi}
\end{align}
where $\binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots,
\alpha_d} = \frac{(\alpha_1 + \alpha_2 + \dots + \alpha_d)!}{\alpha_1! \alpha_2!
\dots \alpha_d!}$ is the multinomial coefficient. It can be easily checked that
$$
k(x,x') = \ip{\phi(x)}{\phi(x')}_{\ell_2}.
$$
The last equality together with the formula for $k$ implies that $k(x,x) <
+\infty$ for any $x$ in $\B(\zero,1)$ and thus in particular implies that $\phi(x)$
indeed lies in $\ell_2$.

@@

\paragraph{Overview.} The idea behind the construction and analysis of the
mapping $\phi$ is polynomial approximation. Specifically, we construct $K$
multivariate polynomials $p_1, p_2, \dots,p_K$ such that
\begin{align}
\label{equation:poly-pos}
& \forall t \in \cbr{1,2,\dots,T}, \qquad p_{y_t}(x_t) \ge \frac{\gamma'}{2} \; ,
\\
\label{equation:poly-neg}
& \begin{gathered}
\forall t \in \cbr{1,2,\dots,T} \ \forall i \in \cbr{1,2,\ldots,K} \setminus \cbr{y_t}, \qquad
p_i(x_t) \le - \frac{\gamma'}{2} \; .
\end{gathered}
\end{align}
We then show (\autoref{lemma:norm-bound}) that each polynomial $p_i$ can be
expressed as $\ip{c_i}{\phi(x)}_{\ell_2}$ for some $c_i \in \ell_2$. This
immediately implies that the examples $(\phi(x_1),y_1), \ldots,
(\phi(x_T),y_T)$ are strongly linearly separable with a positive margin.

>>>>

Consider the classical real separable Hilbert space $\ell_2 = \{ x \in \R^\infty
~:~ \sum_{i=1}^\infty x_i^2 < + \infty \}$ equipped with the standard inner
product $\ip{x}{x'}_{\ell_2} = \sum_{i=1}^\infty x_i x'_i$. If we index the
coordinates of $\ell_2$ by $d$-tuples $(\alpha_1, \dots, \alpha_d)$ of
non-negative integers, the feature map that corresponds to $k$ is $\phi: \B(\zero,1)
\to \ell_2$,
\begin{align}
\begin{split}
&\left(\phi(x_1, x_2, \dots, x_d)\right)_{(\alpha_1, \alpha_2, \dots, \alpha_d)} = \\
& x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d} \cdot \sqrt{2^{-(\alpha_1 + \alpha_2 + \dots + \alpha_d)} \binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots, \alpha_d}}
\end{split}
\label{equation:phi}
\end{align}
where $\binom{\alpha_1 + \dots + \alpha_d}{\alpha_1, \dots,
\alpha_d} = \frac{(\alpha_1 + \dots + \alpha_d)!}{\alpha_1! \dots \alpha_d!}$ is the multinomial coefficient. It can be easily checked that
$$
k(x,x') = \ip{\phi(x)}{\phi(x')}_{\ell_2}.
$$
The last equality together with the formula for $k$ implies that $k(x,x) <
+\infty$ for any $x$ in $\B(\zero,1)$ and thus in particular implies that $\phi(x)$
indeed lies in $\ell_2$.

@@

\paragraph{Overview.} The idea behind the construction and analysis of the
mapping $\phi$ is polynomial approximation. Specifically, we construct $K$
multivariate polynomials $p_1, p_2, \dots,p_K$ such that
\begin{align}
\label{equation:poly-pos}
& \forall t \in \cbr{1,2,\dots,T}, \qquad p_{y_t}(x_t) \ge \frac{\gamma'}{2} \; ,
\\
\label{equation:poly-neg}
& \begin{gathered}
\forall t \in \cbr{1,2,\dots,T} \ \forall i \in \cbr{1,2,\ldots,K} \setminus \cbr{y_t}, \\
p_i(x_t) \le - \frac{\gamma'}{2} \; .
\end{gathered}
\end{align}
We then show (\autoref{lemma:norm-bound}) that each polynomial $p_i$ can be
expressed as $\ip{c_i}{\phi(x)}_{\ell_2}$ for some $c_i \in \ell_2$. This
immediately implies that the examples $(\phi(x_1),y_1), \ldots,
(\phi(x_T),y_T)$ are strongly linearly separable with a positive margin.
